---
title: "TRY1"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: "2022-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The Central Limit Theorem

The Central Limit Theorem (CLT) states that the sample mean of identically distributed independent random variables is approximately normally distributed if the sample size is large. This is true for virtually any distribution! We illustrate the Central Limit Theorem using draws from a Poisson distribution.

We begin recalling that if $x \sim Poisson(\lambda)$, then $E[x] = \lambda$ and $Var[x] = \lambda$, where lambda represents the mean number of events. We illustrate the Central Limit Theorem by simulating 4000 times an experiment in which we take random draws from a Poisson distribution with $\lambda = 35$ for three sample sizes: 15, 50, and 800.

Set-up:

-   sample size 15,50 and 800

-   true $\lambda = 35$

-   so that expected value and variance are both equal to 35

```{r ch1, echo = FALSE}
set.seed(7)
lambdat <- 35
sims <- 4000
m <- c(15,50,800)
E.of.X <- V.of.X <- lambdat
z <- matrix(NA, nrow = sims, ncol = length(m))


for (j in 1:length(m)){
  for (i in 1:sims){
    
    samp <- rpois(n = m[j], lambda = lambdat)
    sample.mean <- mean(samp)
    z[i, j] <- (sample.mean - E.of.X) / sqrt(V.of.X / m[j])
  }
}

summary(z)
```

We then provide some graphical representations

```{r ch2, echo=TRUE, comment=NA}

#### Hystograms and boxplot with ggplot 

z.data <- data.frame(
  val = as.vector(z),
  sample.size = as.factor(rep(m, each = sims))
)

require(ggplot2); require(ggpubr)

# the default boxplot function 

boxplot(z, 
        xlab = "Sample size",
        col = 3:5,
        names = m,
        horisontal = F)

ggplot(data = z.data,
       aes(x = val, fill = sample.size))+
  geom_boxplot()+
  coord_flip()


#### histogram

graph1 <- ggplot(z.data, aes(x = val, 
                   y = stat(density),
                   fill = sample.size))+
  labs(x = 'z', y = 'f(z)')+
  geom_histogram(bins = 80)

graph11 <- graph1 + facet_grid(sample.size ~ .)


##### density estimation 

set.seed(3)
x<- rnorm(1300)
hist(x, breaks = 1000)
plot(density(x))

graph2 <- ggplot(z.data, aes(x = val, fill =  sample.size))+
  geom_density(alpha = .2)

graph22 <- graph2 + facet_grid(sample.size ~ .)


combined.plot <- ggarrange(graph11, 
          graph22,
          ncol = 2,
          common.legend = T,
          legend = "bottom",
          labels = c("Histogram", "Density"))

annotate_figure(
  combined.plot,
  top = text_grob(
    'CLT', color = 'blue', face = 'bold', size = 14
  )
)
```

We calculate and store the Z-score for the mean of each sample size. Note: Recall the command matrix(data,nrow=X, ncol=Y) will create a matrix with X rows and Y columns, and fill those spaces with a vector of data.

Finally, we create three stacked histogram of the Z-scores, one for each sample size, and add the density curve from the standard normal distribution to each histogram. Displaying the distribution of means

```{r ch3, echo=FALSE}
set.seed(6)
hist(rnorm(10^4))
```

Let us also provide a brief distribution of the data

```{r ch4, echo=TRUE, comment=NA}
summary(rgeom(100, 0.7))
```
